apply flashr2 with OCV

### 2018-01-25 analysis/templateforOCV.Rmd
Files commited by wflow_commit.

Here you need change the `\"addpath(\'~/HG/flash/data/OCVmissflashr2/Breastcancer\');` to your folder which contains `missvalue.m` file. this file name is `wrapper.R`

@@

@@

RMSE = sqrt(sum(SSE)/(100000));
RMSE;

@@

you need change the path as well. this file name is 'missvalue.m'

@@

```{r}
library(ggplot2)
plot_res = function(output,title = "data",legend_position = "none", x_label){
  rmse = as.vector(output)
  N = dim(output)[1]
  # methods = rep(c("flash","NBSFA","PMD","softImpute"), each = N)
  methods = rep(x_label, each = N)
  df = data.frame(RMSE = rmse, Method = methods )
  p<-ggplot(df, aes(x=Method, y=RMSE, color=Method)) +
  geom_boxplot()+
  # geom_violin()+
  ggtitle(title) +  theme_bw()+
    theme(legend.position= legend_position, legend.text=element_text(size=15), axis.text.y = element_text(size =6))
  p
}
x_label = c("flash","NBSFA","PMD","softImpute")
PT_res = readRDS("../data/missingvalue/OCVtemplate/RCCres/president_box.rds")
pp = plot_res(PT_res,"Text data",x_label = x_label)
DT_res = readRDS("../data/missingvalue/OCVtemplate/RCCres/denoiseRtumor_box.rds")
pd = plot_res(DT_res,"Tumor data",x_label = x_label)
GZ_res = readRDS("../data/missingvalue/OCVtemplate/RCCres/gtexzscore_box.rds")
pg = plot_res(GZ_res,"GTEx data",x_label = x_label)
BC_res = readRDS("../data/missingvalue/OCVtemplate/RCCres/BreastCancer_box.rds")
pb = plot_res(BC_res,"Breast Cancer data",x_label = x_label)
ML_res = readRDS("../data/missingvalue/OCVtemplate/RCCres/ML100K_box.rds")
ML_res[c(2,13,17,21,29,37,62,76,77,93,95,100),] = NA
ML_res = matrix(as.numeric(ML_res),ncol = 4)
pM = plot_res(ML_res,"Movie Lens data",x_label = x_label)
```

## plots

```{r}
gridExtra::grid.arrange(pp,pd,pg,pb,pM, layout_matrix = rbind(c(1,NA,2),c(NA,5,NA),c(4,NA,3)))
```

## results for different tuning parameters

```{r}
pmd_c = sapply(seq(1,10),function(x){paste("PMD",x)})
softImpute_c = sapply(seq(1,10),function(x){paste("SF",x)})
x_label= c("flash","NBSFA",pmd_c,softImpute_c)
PT_res = readRDS("../data/missingvalue/box_res_grids_sf_pmd/denoiseTumor_box.rds")
pt = plot_res(PT_res,"Tumor data",x_label = x_label)
pt
PT_res = readRDS("../data/missingvalue/box_res_grids_sf_pmd/TEXT_prsdt_box.rds")
pp = plot_res(PT_res,"Text data",x_label = x_label)
pp
```

## use OCV choose the tuning parameters

labels | null check | backfitting | greedy | ebnm_ash | ebnm_pn 
------ | ---------- | ----------- | ------ | -------- | ------
flashG | yes| |yes | yes |
flashGwn | | | yes|yes |
flashB | yes| yes| | yes|
PN | yes | | yes| |yes

### Breast Cancer data

we use 10 grids for `softImpute` and `PMD`

```{r}
PB_res = readRDS("../data/missingvalue/testingcode/box_Breast.rds")
x_label= c("PN","flashG","flashGwn","flashB","nsfa","pmd","soft")
pb = plot_res(PB_res,"Breast Cancer data",x_label = x_label)
pb
```

we take the 'flashB' away to compare the rest.

```{r}
x_label= c("PN","flashG","flashGwn","nsfa","pmd","soft")
pb = plot_res(PB_res[,-4],"Breast Cancer data",x_label = x_label)
pb
```

### denoiseR Tumor data

we use 10 grids for `softImpute` and `PMD`

```{r}
PT_res = readRDS("../data/missingvalue/testingcode/box_denoiseTumor.rds")
x_label= c("PN","flashG","flashGwn","flashB","nsfa","pmd","soft")
pt = plot_res(PT_res,"Tumor data",x_label = x_label)
pt
```

### text data

in this data, we add `zero` as use zero values as imputation to compare with other methods.

```{r}
PT_res = readRDS("../data/missingvalue/testingcode/box_president.rds")
x_label= c("PN","flashG","flashGwn","flashB","nsfa","pmd","soft","zero")
pt = plot_res(PT_res,"Text data",x_label = x_label)
pt
```

>>>>

This file name is `wrapper.R`

@@

In this folder

@@

RMSE = sqrt(sum(SSE)/(settings.D*settings.N));
RMSE;

@@

you need change the path `~/HG/flash/data/missingvalue/methods/NBSF/nsfa-master/` and `~/HG/flash/data/missingvalue/methods/NBSF/nsfa-master/utils/` which have the NBSFA matlab code.

@@

```{r}
# this is the independent result

library(ggplot2)
plot_res = function(output,title = "data",legend_position = "none", x_label){
  rmse = as.vector(output)
  N = dim(output)[1]
  methods = rep(x_label, each = N)
  df = data.frame(RMSE = rmse, Method = methods )
  p<-ggplot(df, aes(x=Method, y=RMSE, color=Method)) +
    geom_boxplot()+
    # geom_violin()+
    ggtitle(title) +  theme_bw()+
    theme(legend.position= legend_position, legend.text=element_text(size=15),
          plot.title = element_text(size = 15, face = "bold"),
          axis.text.y = element_text(size =12.6),
          axis.text.x = element_text(size =12.6,angle = 45, hjust = 1))
  p
}

setwd("~/HG/flash_workflow/analysis")

##############  MovieLens data

ML_res = readRDS("../data/missingvalue/OCVtemplate/RCCres/ML100K_box.rds")
ML_res[c(2,13,17,21,29,37,62,76,77,93,95,100),] = NA
ML_res = matrix(as.numeric(ML_res),ncol = 4)
# c("flash","NBSFA","PMD","softImpute")
ml_res = readRDS("../data/missingvalue/OCVtemplate/RCCres/OCVNew20rep/movies100K/boxplot_cv.rds")
# flashG_rmse,flashGwn_rmse,pmd_rmse,soft_rmse
ml_res[1:20,] = sqrt((ml_res[1:20,])^2 * (943*1682)/(100000))
ml_res = ml_res[1:20,]
ML_res = ML_res[-c(2,13,17,21,29,37,62,76,77,93,95,100),]
ML_res = ML_res[1:20,]
# add PN result
ML_pn_res = readRDS("../data/missingvalue/OCVtemplate/RCCres/OCVNew20rep/movies100K/box_cv_pn.rds")
# the result order would be flashG PMD PMDcv NSFA SF SFcv
output = cbind(ML_pn_res[,1],ML_pn_res[,2],ML_res[,3],ml_res[,3],ML_res[,2],ML_res[,4],ml_res[,4])

x_label= c("flash","flash.pn","PMD","PMD.cv1","NBSFA","SI","SI.cv")
plotM = plot_res(output,"MovieLens data",x_label = x_label)

############ Breast Cancer data

BC_res = readRDS("../data/missingvalue/OCVtemplate/RCCres/BreastCancer_box.rds")
BC_res = BC_res[1:20,]
# c("flash","NBSFA","PMD","softImpute")
bc_res = readRDS("../data/missingvalue/testingcode/box_Breast.rds")
# c("PN","flashG","flashGwn","flashB","nsfa","pmd","soft")

# the result order would be flashG PMD PMDcv NSFA SF SFcv
output = cbind(bc_res[,2],bc_res[,1],BC_res[,3],bc_res[,6],BC_res[,2],BC_res[,4],bc_res[,7])
x_label= c("flash","flash.pn","PMD","PMD.cv1","NBSFA","SI","SI.cv")
plotB = plot_res(output,"Breast Cancer data",x_label = x_label)

############ GTEx data

GZ_res = readRDS("../data/missingvalue/OCVtemplate/RCCres/gtexzscore_box.rds")
GZ_res = GZ_res[1:20,]
# c("flash","NBSFA","PMD","softImpute")
gz_res = readRDS("../data/missingvalue/OCVtemplate/RCCres/OCVNew20rep/gtexzscore/box_cv.rds")
# flashG_rmse,nsfa_rmse,pmd_rmse,soft_rmse
gz_pn_res = readRDS("../data/missingvalue/OCVtemplate/RCCres/OCVNew20rep/gtexzscore/box_pn.rds")
gz_pn_res[c(23,25,29,34),] = NA
gz_pn_res = matrix(as.numeric(gz_pn_res[21:40,]),ncol = 2)

# the result order would be flashG PMD PMDcv NSFA SF SFcv
output = cbind(gz_res[,1],gz_pn_res[,2],GZ_res[,3],gz_res[,3],GZ_res[,2],GZ_res[,4],gz_res[,4])
x_label= c("flash","flash.pn","PMD","PMD.cv1","NBSFA","SI","SI.cv")
plotG = plot_res(output,"GTEx data",x_label = x_label)

############ Text data

PT_res = readRDS("../data/missingvalue/OCVtemplate/RCCres/president_box.rds")
PT_res = PT_res[1:20,]
# c("flash","NBSFA","PMD","softImpute")
pt_res = readRDS("../data/missingvalue/testingcode/box_president.rds")
# c("PN","flashG","flashGwn","flashB","nsfa","pmd","soft","zero")

# the result order would be flashG PMD PMDcv NSFA SF SFcv
output = cbind(pt_res[,3],pt_res[,1],PT_res[,3],pt_res[,6],PT_res[,2],PT_res[,4],pt_res[,7])
x_label= c("flash","flash.pn","PMD","PMD.cv1","NBSFA","SI","SI.cv")
plotP = plot_res(output,"Text data",x_label = x_label)

############ Tumor data

DT_res = readRDS("../data/missingvalue/OCVtemplate/RCCres/denoiseRtumor_box.rds")
DT_res = DT_res[1:20,]
# c("flash","NBSFA","PMD","softImpute")
dt_res = readRDS("../data/missingvalue/testingcode/box_denoiseTumor.rds")
# c("PN","flashG","flashGwn","flashB","nsfa","pmd","soft")

# the result order would be flashG PMD PMDcv NSFA SF SFcv
output = cbind(dt_res[,2],dt_res[,1],DT_res[,3],dt_res[,6],DT_res[,2],DT_res[,4],dt_res[,7])
x_label= c("flash","flash.pn","PMD","PMD.cv1","NBSFA","SI","SI.cv")
plotT = plot_res(output,"Tumor data",x_label = x_label)

# gridExtra::grid.arrange(plotP,plotT,plotG,plotB,plotM, layout_matrix = rbind(c(1,NA,2),c(NA,5,NA),c(4,NA,3)))
gridExtra::grid.arrange(plotM,plotT,plotG,plotB,plotP, layout_matrix = rbind(c(1,2,3),c(4,5,NA) ))
